Lasso_RCI_Response

### 2024-02-05 Lasso_RCI_Response.Rmd
Correlation table

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
head(df)

# source("~/Desktop/Coding/R working directory/Hospital_Visualizations/Lasso_RCI_Source.R")
```

@@

```{r}
# 1. Re-coding / Renaming variables ------------------------------------------
# We can change the current variables to make them easier to interpret.

@@

@@

@@

@@

@@

@@

                     Referral_1 = as.factor(Referral_1),
                     Referral_1 = recode(Referral_1,
                                         "1" ="Inpatient",
                                         "2" ="PHP",
                                         "3" ="APS",
                                         "4" ="Psychatrist",
                                         "5" ="PCP",
                                         "6" ="Another Physican",
                                         "7" ="Therapist",
                                         "17"="Other",

                     #Lets make some new variables 
                     #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                              ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                                     ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3",
                                            ifelse(is.na(Days_complete_1), NA, "4"
                                            ))))),
                     Duration_lab = as.factor(recode(Duration,
                                                     "1"="1-5",
                                                     "2"="6-10",
                                                     "3"="11-15",
                                                     "4"="16+"
                     )),
                     Duration_10 = as.factor(
                       ifelse(Duration == 1 | Duration == 2, "1",
                              ifelse(Duration == 3 | Duration == 4, "2", NA)
                       )))

@@

Mothership_Diag_treat <- Mothership |>
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

@@

library(JTRCI)
library(ClinicalSig)

#devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

## Part 1: Who is attending?
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of prepost change???
- Table 4: demographic breakdown
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),
         !is.na(RESPONDER_FIGS)
        )

@@

# Treatment info
resp_tab <- data.frame(table1::table1(
  ~Referral_1 + DC_status_1 + RIPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab

# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | RESPONDER_FIGS, 
                                     data = Mothership_post))
Dis_tab

#Full demographic break down.
CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
CODis_tab

Mothership_post$Current_Dx
```

```{r}
#Treatment Scores

  # I'm imagining a table that has all of the averages under 3 columns 
      # Pre, post, delta | (mean, SD)
  # variables involved = 
      # CUXOS, CUDOS, RDQ, 
  # can I make this break up by treatment response?

resp_tab <- data.frame(table1::table1(
  ~CUXOS_pre + CUXOS_post + Delta_Anx_DC + CUXOS_pre + CUXOS_post + Delta_Anx_DC +   | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab

View(Mothership_post)

#Read in a New Data Set
Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))

#Make This Data Set Long Data
library(tidyr)
Mothership_Long_RDQ <- gather(Mothership_Diag_treat,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

#Create a Time Variable
Mothership_Long_RDQ$PrePost <- NA
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"

#Create a New Data Set with an Average Depression Variable and Race
Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
  group_by(rm,PrePost) %>%
  summarise(RDQ=mean(RDQ,na.rm=TRUE))

#Add a Paired Variable to the New Data Set
Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
                            paired=case_when(rm=="rdqPRE_coping"~"1",
                                             rm=="rdqPOST_coping"~"1",
                                             rm=="rdqPRE_pmh"~"2",
                                             rm=="rdqPOST_pmh"~"2",
                                             rm=="rdqPRE_func"~"3",
                                             rm=="rdqPOST_func"~"3",
                                             rm=="rdqPRE_wbs"~"4",
                                             rm=="rdqPOST_wbs"~"4",
                                             rm=="rdqPRE_sym"~"5",
                                             rm=="rdqPOST_sym"~"5"))

Mothership_Mean_RDQ[,1] = c("Coping","PMH","Functioning","WBS","Symptoms","Coping","PMH","Functioning","WBS","Symptoms")

wide_rdq <- Mothership_Mean_RDQ |>
  pivot_wider(
    names_from = PrePost, values_from = RDQ
  ) |>
  select(
    rm,Pre,Post
  )

#Table
wide_rdq

@@

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}

@@

## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression
```{r}

>>>>

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")

@@

```{r}
# 1. Re-coding / Renaming variables ------------------------------------------
# We can change the current variables to make them easier to interpret.
str(Mothership_post$Education_1)

@@

                     Some_College = Education_1,
                     Some_College = recode(Education_1,
                                          "<Grade 12" = "No College",
                                          "<Grade 12" = "No College",
                                          "HS Diploma or GED" = "No College",
                                          "HS Diploma or GED" = "No College",
                                          "Some College/Associates Degree" = "Some College",
                                          "Some College/Associates Degree" = "Some College",
                                          "Bachelors Degree" = "Some College",
                                          "Bachelors Degree" = "Some College",
                                          "Grad Degree" ="Some College"),

@@

                     Female = Gender_1,
                     Female= recode(Gender_1,
                                       "Female" = "Female",
                                       "Male" = "Not",
                                       "Non-Binary" = "Not",
                                       "Other" = "Not",
                                       "Other" = "Not"),

@@

                     Married = recode(Relationship_1,
                                             "Married or Cohabitating" = "Married or Cohabitating",
                                             "Widowed or Separated" = "Not",
                                             "Divorced" = "Not",
                                             "Single or Never Married" = "Not"),

@@

                     Straight = recode(Sexuality_1,
                                         "Straight" = "Straight",
                                          "Gay" = "Not Straight",
                                          "Bisexual" = "Not Straight",
                                          "Other" = "Not Straight"),

@@

                     White = recode(Race_1,
                                     "White" = "White",
                                     "Black" = "Not White",
                                     "Hispanic"="Not White",
                                     "Asian"="Not White",
                                     "Portugese"="Not White",
                                     "Other"="Not White"),

@@

                     Discharge = recode(DC_status_1,
                                          "Treatment Complete" = "Treatment Successful",
                                          "Treatment nearly complete" = "Treatment Successful",
                                          "Insurance no longer covering" = "Other",
                                          "Nonattendance" = "Other",
                                          "Inappropriate (language)/Referred to another tx setting" ="Other",
                                          "Transferred to inpatient"="Other",
                                          "Withdrew due to external limitations"="Other",
                                          "Withdrew AMA"="Other",
                                          "Other"="Other",
                                          "Other"="Other",
                                          "Other"="Other"),
#Lets make some new variables 
                     #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                              ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                                     ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3",
                                            ifelse(is.na(Days_complete_1), NA, "4"
                                            ))))),
                     Duration_lab = as.factor(recode(Duration,
                                                     "1"="1-5",
                                                     "2"="6-10",
                                                     "3"="11-15",
                                                     "4"="16+")),
                     Duration_10 = as.factor(
                       ifelse(Duration == 1 | Duration == 2, "1",
                              ifelse(Duration == 3 | Duration == 4, "2", NA)
                       )))

@@

# Mothership_Diag_treat <- Mothership |>
#   filter(!is.na(Disorder_treat),
#          !is.na(TxYear),
#          !is.na(Duration))

@@

library(JTRCI)
# library(ClinicalSig)
# 
# #devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

## Part 1: Who is attending?

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),
         !is.na(RESPONDER_FIGS)
        )

@@

Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
Simple_Demo_tab
```

### Treatment information
Overal look at treatment varaibles by treatment response
```{r}
# PHP Treatment information
resp_tab <- data.frame(table1::table1(
   ~ DC_status_1 + IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab
```

pre-post scores by treatment response
```{r}
# Treatment scores
#1. Make DF + name columns
Scores_tab <- data.frame(matrix(nrow = 9 ,ncol=7))
colnames(Scores_tab) = c("Variables", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)")

#2. Row 1 - responders
Scores_tab[1,] = c(NA,"Non-responder","Non-responder","Non-responder","Responder","Responder","Responder")

#3. Get statistics for variables + Assign to table
  # Anxiety - CUXOS
    #make df
      anx_rep_tab <- Mothership_post |>
        group_by(RESPONDER_FIGS) |>
        summarize(pre_anx = round(mean(CUXOS_pre, na.rm = TRUE),2),
                  pre_anx_sd = round(sd(CUXOS_pre, na.rm = TRUE),2),
                  post_anx = round( mean(CUXOS_post,na.rm = TRUE),2),
                  post_anx_sd = round( sd(CUXOS_post,na.rm = TRUE),2),
                  delta_anx = round( mean(Delta_Anx_DC,na.rm = TRUE),2),
                  delta_anx_sd = round( sd(Delta_Anx_DC, na.rm = TRUE),2)
                  )
# add to scores tab
        Scores_tab[2,] = c(
          "CUXOS",
          #Non-responder scores
          paste0(anx_rep_tab$pre_anx[[1]]," (",anx_rep_tab$pre_anx_sd[[1]],")"),
          paste0(anx_rep_tab$post_anx[[1]]," (",anx_rep_tab$post_anx_sd[[1]],")"),
          paste0(anx_rep_tab$delta_anx[[1]]," (",anx_rep_tab$delta_anx_sd[[1]],")"),
          #responder scores
          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")")
        )

  # Depression - CUDOS
  #Make df
    dep_rep_tab <- Mothership_post |>
      group_by(RESPONDER_FIGS) |>
      summarize(pre_dep = round( mean(CUDOS_pre, na.rm = TRUE),2),
                pre_dep_sd = round( sd(CUDOS_pre, na.rm = TRUE),2),
                post_dep = round( mean(CUDOS_post, na.rm = TRUE),2),
                post_dep_sd = round( sd(CUDOS_post, na.rm = TRUE),2),
                delta_dep = round( mean(Delta_Dep_DC, na.rm = TRUE),2),
                delta_dep_sd = round( sd(Delta_Dep_DC, na.rm = TRUE),2)
                )
    #Add to Scores_tab
       Scores_tab[3,] = c(
        "CUDOS",
        #Non-responder scores
        paste0(dep_rep_tab$pre_dep[[1]]," (",dep_rep_tab$pre_dep_sd[[1]],")"),
        paste0(dep_rep_tab$post_dep[[1]]," (",dep_rep_tab$post_dep_sd[[1]],")"),
        paste0(dep_rep_tab$delta_dep[[1]]," (",dep_rep_tab$delta_dep_sd[[1]],")"),
        #responder scores
        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")")
      )

  #RDQ subscales
       Scores_tab[4,1] = "RDQ Subscales"

  # Coping
      cope_rep_tab <- Mothership_post |>
        group_by(RESPONDER_FIGS) |>
        summarize(pre_cope = round( mean(rdqPRE_coping, na.rm = TRUE),2),
                  pre_cope_sd = round( sd(rdqPRE_coping, na.rm = TRUE),2),
                  post_cope = round( mean(rdqPOST_coping, na.rm = TRUE),2),
                  post_cope_sd = round( sd(rdqPOST_coping, na.rm = TRUE),2),
                  delta_cope = round( mean(rdq_coping_change, na.rm = TRUE),2),
                  delta_cope_sd = round( sd(rdq_coping_change, na.rm = TRUE),2)
              )
      Scores_tab[5,] = c(
        "Coping",
        #Non-responder scores
        paste0(cope_rep_tab$pre_cope[[1]]," (",cope_rep_tab$pre_cope_sd[[1]],")"),
        paste0(cope_rep_tab$post_cope[[1]]," (",cope_rep_tab$post_cope_sd[[1]],")"),
        paste0(cope_rep_tab$delta_cope[[1]]," (",cope_rep_tab$delta_cope_sd[[1]],")"),
        #responder scores
        paste0(cope_rep_tab$pre_cope[[2]]," (",cope_rep_tab$pre_cope_sd[[2]],")"),
        paste0(cope_rep_tab$post_cope[[2]]," (",cope_rep_tab$post_cope_sd[[2]],")"),
        paste0(cope_rep_tab$delta_cope[[2]]," (",cope_rep_tab$delta_cope_sd[[2]],")")
      )
   # Positive mental health
  pmh_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_pmh = round( mean(rdqPRE_pmh, na.rm = TRUE),2),
              pre_pmh_sd = round( sd(rdqPRE_pmh, na.rm = TRUE),2),
              post_pmh = round( mean(rdqPOST_pmh, na.rm = TRUE),2),
              post_pmh_sd = round( sd(rdqPOST_pmh, na.rm = TRUE),2),
              delta_pmh = round( mean(rdq_pmh_change, na.rm = TRUE),2),
              delta_pmh_sd = round( sd(rdq_pmh_change, na.rm = TRUE),2)
              )
         Scores_tab[6,] = c(
              "Positive Mental Health",
              #Non-responder scores
              paste0(pmh_rep_tab$pre_pmh[[1]]," (",pmh_rep_tab$pre_pmh_sd[[1]],")"),
              paste0(pmh_rep_tab$post_pmh[[1]]," (",pmh_rep_tab$post_pmh_sd[[1]],")"),
              paste0(pmh_rep_tab$delta_pmh[[1]]," (",pmh_rep_tab$delta_pmh_sd[[1]],")"),
              #responder scores
              paste0(pmh_rep_tab$pre_pmh[[2]]," (",pmh_rep_tab$pre_pmh_sd[[2]],")"),
              paste0(pmh_rep_tab$post_pmh[[2]]," (",pmh_rep_tab$post_pmh_sd[[2]],")"),
              paste0(pmh_rep_tab$delta_pmh[[2]]," (",pmh_rep_tab$delta_pmh_sd[[2]],")")
            )
   # Functioning
  func_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_func = round( mean(rdqPRE_func, na.rm = TRUE),2),
              pre_func_sd = round( sd(rdqPRE_func, na.rm = TRUE),2),
              post_func = round( mean(rdqPOST_func, na.rm = TRUE),2),
              post_func_sd = round( sd(rdqPOST_func, na.rm = TRUE),2),
              delta_func = round( mean(rdq_func_change, na.rm = TRUE),2),
              delta_func_sd = round( sd(rdq_func_change, na.rm = TRUE),2)
              )    
         Scores_tab[7,] = c(
              "Functioning",
              #Non-responder scores
              paste0(func_rep_tab$pre_func[[1]]," (",func_rep_tab$pre_func_sd[[1]],")"),
              paste0(func_rep_tab$post_func[[1]]," (",func_rep_tab$post_func_sd[[1]],")"),
              paste0(func_rep_tab$delta_func[[1]]," (",func_rep_tab$delta_func_sd[[1]],")"),
              #responder scores
              paste0(func_rep_tab$pre_func[[2]]," (",func_rep_tab$pre_func_sd[[2]],")"),
              paste0(func_rep_tab$post_func[[2]]," (",func_rep_tab$post_func_sd[[2]],")"),
              paste0(func_rep_tab$delta_func[[2]]," (",func_rep_tab$delta_func_sd[[2]],")")
            )

    # General sense of wellbeing
    wbs_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_wbs = round( mean(rdqPRE_wbs, na.rm = TRUE),2),
              pre_wbs_sd = round( sd(rdqPRE_wbs, na.rm = TRUE),2),
              post_wbs = round( mean(rdqPOST_wbs, na.rm = TRUE),2),
              post_wbs_sd = round( sd(rdqPOST_wbs, na.rm = TRUE),2),
              delta_wbs = round( mean(rdq_wbs_change, na.rm = TRUE),2),
              delta_wbs_sd = round( sd(rdq_wbs_change, na.rm = TRUE),2)
              )

     Scores_tab[8,] = c(
              "General sense of wellbeing",
              #Non-responder scores
              paste0(wbs_rep_tab$pre_wbs[[1]]," (",wbs_rep_tab$pre_wbs_sd[[1]],")"),
              paste0(wbs_rep_tab$post_wbs[[1]]," (",wbs_rep_tab$post_wbs_sd[[1]],")"),
              paste0(wbs_rep_tab$delta_wbs[[1]]," (",wbs_rep_tab$delta_wbs_sd[[1]],")"),
              #responder scores
              paste0(wbs_rep_tab$pre_wbs[[2]]," (",wbs_rep_tab$pre_wbs_sd[[2]],")"),
              paste0(wbs_rep_tab$post_wbs[[2]]," (",wbs_rep_tab$post_wbs_sd[[2]],")"),
              paste0(wbs_rep_tab$delta_wbs[[2]]," (",wbs_rep_tab$delta_wbs_sd[[2]],")")
            )

    #Symptoms
    sym_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_sym = round( mean(rdqPRE_sym, na.rm = TRUE),2),
              pre_sym_sd = round( sd(rdqPRE_sym, na.rm = TRUE),2),
              post_sym = round( mean(rdqPOST_sym, na.rm = TRUE),2),
              post_sym_sd = round( sd(rdqPOST_sym, na.rm = TRUE),2),
              delta_sym = round( mean(rdq_sym_change, na.rm = TRUE),2),
              delta_sym_sd = round( sd(rdq_sym_change, na.rm = TRUE),2)
              )

      Scores_tab[9,] = c(
              "Symptoms",
              #Non-responder scores
              paste0(sym_rep_tab$pre_sym[[1]]," (",sym_rep_tab$pre_sym_sd[[1]],")"),
              paste0(sym_rep_tab$post_sym[[1]]," (",sym_rep_tab$post_sym_sd[[1]],")"),
              paste0(sym_rep_tab$delta_sym[[1]]," (",sym_rep_tab$delta_sym_sd[[1]],")"),
              #responder scores
              paste0(sym_rep_tab$pre_sym[[2]]," (",sym_rep_tab$pre_sym_sd[[2]],")"),
              paste0(sym_rep_tab$post_sym[[2]]," (",sym_rep_tab$post_sym_sd[[2]],")"),
              paste0(sym_rep_tab$delta_sym[[2]]," (",sym_rep_tab$delta_sym_sd[[2]],")")
            )
Scores_tab
```

### Disorder Breakdowns
Here are some tables displaying info on the psychiatric disorders treated at the PHP
```{r}
# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | RESPONDER_FIGS, 
                                     data = Mothership_post))
colnames(Dis_tab) = c("Variables","Non Responder", "Responder", "Total")
Dis_tab

#Full demographic break down
co_dis_tab <- Mothership_Diag_treat |>
  pivot_longer(
    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat))

CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
colnames(CODis_tab)[1] = c("Variables")
CODis_tab
```

@@

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
cor_tab<- Mothership_post |>
  select( c(
    # Demographics
    Age_1,Some_College:Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, # Days_noshow_1, Days_not_attended_1, Days_cancel_1,
    # Disorders
    Mood_D:Other,Co_Anx:Co_Trauma,Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_sym_change

  ))

#comments about what I should do
      #Should I make a level of anxiety / depression - cuxos cut offs?
      # should I use the first score or the pre score?
      # Should I do each individual disorder, or just the overarching classes (i.e., depression)?
      # should I include co_occuring even if there is a lot of overlap (i.e., depressive P and Co)

# View(cor_tab)
# View(Mothership_post)

# install.packages("ggcorrplot")
# library(ggcorrplot)
model.matrix(~0+., data=cor_tab) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

@@

## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression
```{r}
DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "Anxeity: JT indices by disorder")
